\cvsection{Experience}

\begin{cventries}

    \cventry
    {Senior Devops Engineer}
    {KI Challenge.rs GmbH}
    {Berlin, Germany}
    {Nov. 2020 - Dec. 2021}
    {
        \begin{cvitems}
            \item Worked on the greenfield cloud infrastructure of an e-commerce portal for an automotive corporation.
        \end{cvitems}
    }

    \cventry
    {Team Lead \& Senior Infrastructure Engineer}
    {KI Challenge.rs GmbH}
    {Berlin, Germany}
    {Nov. 2020 - Dec. 2021}
    {
        \begin{cvitems}
            \item {\textbf{Project:} \href{https://cloudmobility.io}{cloudmobility} - Daimler AG}
        \end{cvitems}
    }

    \cventry
    {Team Lead \& Senior Infrastructure Engineer}
    {MobiLab Solutions GmbH}
    {Berlin, Germany}
    {Jul. 2018 - May 2020}
    {
    \begin{cvitems}
        \item {\textbf{Project:} \href{https://cloudmobility.io}{cloudmobility} - Daimler AG}
        \newline
        \item {Lead the \textbf{Platform Infrastructure} team who was responsible of the compute,
        storage and network domains of the Kubernetes and Ceph based multi-tenant cloud platform.}
        \item {Lead the architectural decision processes on compute, storage and network components.}
        \item {Communicated with the other team leads on defining the API contracts between the teams.}
        \item {Wrote design proposals and decision logs for the platform infrastructure.}
        \item {Established \& documented coding guidelines for the Ansible playbook repositories.}
        \item {Implemented Ansible playbooks to bring up multi-tenant, production-grade Kubernetes clusters.}
        \item {Created Helm charts for the management toolset of the Kubernetes clusters.}
        \smallskip
        \item {
        \textbf{Technologies used:} Kubernetes (kubeadm, CRDs and custom controllers,
        PodSecurityPolicies, RBAC, Admission Webhooks, dynamic persistence provisioners),
        Containerd, Docker, Helm, Istio, Cilium, Nginx Ingress, Ansible, Go,
        HAProxy, Keepalived, CEPH, MAAS, BGP, KVM, gVisor, AppArmor, bare-metal servers.
        }
    \end{cvitems}
    }

    \cventry
    {System \& Cloud Administrator}
    {}
    {}
    {May 2018 - May 2020}
    {
    \begin{cvitems}
        \item {
        Migrated various applications that are running on Azure to Google Cloud,
        to managed Kubernetes clusters and other managed GCP resources.
        }
        \item {Identity Access Management of the cloud resources on Azure and Google Cloud.}
    \end{cvitems}
    }

    \cventry
    {Senior Kubernetes \& Devops Consultant}
    {}
    {}
    {Mar. 2018 - Apr. 2018}
    {
    \begin{cvitems}
        \item {
        \textbf{Project:} \href{https://www.daimler-mobility.com/en/solutions/mobility-ecosystem/portfolio/payment-services/}{Mercedes pay} - Daimler AG
        }
        \newline
        \item {Worked on the payment provider system as a technical Kubernetes and devops consultant.}
        \item {Assisted the team with managing their deployments on Kubernetes.}
        \item {
        Set up and configured the monitoring and logging components, database backups,
        Helm charts, build pipelines.
        }
        \smallskip
        \item {
        \textbf{Technologies used:} Kubernetes (with no-root policy and other restrictions,
        NetworkPolicies, Ingresses), Helm, EFK, Prometheus,
        Grafana, AlertManager, PostgreSQL, Traefik.
        }
    \end{cvitems}
    }

    \cventry
    {Engineering Lead}
    {}
    {}
    {Jan. 2018 - May 2020}
    {
    \begin{cvitems}
        \item {
        Worked on establishing the engineering practices in the company while
        collaborating with the other leads. Documenting these practices.
        }
        \item {
        Worked on defining the recruitment process, preparing technical challenges
        and conducting technical interviews.
        }
    \end{cvitems}
    }

    \cventry
    {Branch Manager}
    {}
    {}
    {Oct. 2017 - May 2020}
    {
    \begin{cvitems}
        \item {Recruitment for the Berlin office}
        \item {Budget planning}
        \item {People \& resource management}
    \end{cvitems}
    }

    \cventry
    {Team Lead \& Senior Backend Engineer}
    {}
    {}
    {Mar. 2017 - Feb. 2018}
    {
    \begin{cvitems}
        \item {
        \textbf{Project:} Master Data Management Platform - Metro AG
        }
        \newline
        \item {
        Lead a team on building a Master Data Management platform that allowed product attribute validation and enrichment.
        }
        \item {
        Developed microservices using Kotlin \& Spring Boot that run on Kubernetes.
        }
        \item {
        Designed and implemented a fuzzy search with autocomplete on all master data items using Apache Solr.
        }
        \item {
        Designed the data model for Cassandra to ensure that the data is evenly distributed and fetched optimally.
        }
        \item {
        Implemented on-the-fly XML<>JSON transformation for integration with the legacy systems.
        }
        \smallskip
        \item {
        \textbf{Technologies used:} Java 8, REST, Kotlin, Spring Boot, Hystrix, Zuul, Cassandra,
        Solr, Docker, microservices, Kubernetes, Jenkins.
        }
    \end{cvitems}
    }

    \cventry
    {Backend Engineer}
    {}
    {}
    {Oct. 2015 - Feb. 2017}
    {
    \begin{cvitems}
        \item {\textbf{Project:} Article Cache - Metro AG}
        \item {
        Worked on a central master data storage system that has acted as a data streaming platform.
        }
        \item {
        Implemented a persistent queue on a distributed filesystem using Java concurrency API and file locks.
        }
        \item {
        Implemented a rotating XML storage to circumvent the restrictions of HDFS.
        }
        \smallskip
        \item {\textbf{Technologies used:} Java, GPFS, WebLogic, JAX-RS, Oracle DB}
        \medskip
        \item {\textbf{Project:} Up to Growth! - Metro AG}
        \item {
        Worked on the backend of a mobile application that aims to increase productivity of meetings.
        }
        \smallskip
        \item {\textbf{Technologies used:} Java, Spring, Azure SQL, Azure Blob Storage.}
    \end{cvitems}
    }

    \cventry
    {Software Developer}
    {Turkish Armed Forces}
    {Ankara, Turkey}
    {Mar. 2015 - Sep. 2015}
    {
    \begin{cvitems}
        \item{Completed the compulsory military service.}
        \item{Developed small scoped desktop apps to assist various departments.}
        \item{Provided limited IT support.}
    \end{cvitems}
    }

    \cventry
    {Backend Engineer}
    {Imona Technologies Ltd.}
    {Istanbul, Turkey}
    {Jan. 2013 - Mar. 2015}
    {
    \begin{cvitems}
        \item {\textbf{Project:} ImonaCloud Platform}
        \item {Worked on the development of an app-PaaS consists of an in-browser
        cloud application development platform \& marketplace.}
        \item{Was responsible for installation, preparation of environment (Java Runtime, Application Server,
        Web Server, Load-Balancing, Database, Firewall, Forwarding etc.) and
        maintenance of more than 15 Linux (Ubuntu) servers.}
        \item{Was responsible for installation of continuous integration tools, build automation and deployments.}
        \smallskip
        \item {\textbf{Technologies used:} Java, Vaadin, Hibernate, Tomcat, Ubuntu, MVEL.}
    \end{cvitems}
    }

    \cventry
    {Intern}
    {Vodafone Turkey}
    {Istanbul, Turkey}
    {Jul. 2011 - Feb. 2012}
    {
    \begin{cvitems}
        \item {Worked on the Data Warehouse, Data Quality department.}
    \end{cvitems}
    }

    \cventry
    {Intern}
    {IBM Turkey}
    {Istanbul, Turkey}
    {Jul. 2010}
    {
    \begin{cvitems}
        \item {Worked with Java EE Technologies: JSP, JSF.}
    \end{cvitems}
    }

\end{cventries}
